|

### 2025-02-14 output/seminar-slideshow.qmd
Correct MDISC and discrimination super-indexes

@@

::: fragment
$$
  \begin{align}
    MDISC^*_1 &= \sqrt{
        [1, 1]
        \begin{bmatrix}
          1 \\
          1
        \end{bmatrix}
      } \\
      &= \sqrt{ 1 · 1 + 1 · 1 } \\
      &= \sqrt{ 1 + 1 } \\
      &= \sqrt{ 2 } \\
      &\approx 1.41
  \end{align}
$$
:::
:::::
:::::::

>>>>

mirt_item_coords |>
  ggplot(
    aes(
      origin_1, origin_2,
      xend = end_1,
      yend = end_2,
      color = factor(item), fill = factor(item)
    ),
  )                                                  +
  geom_vline(xintercept = 0, linewidth = GRID_WIDTH) +
  geom_hline(yintercept = 0, linewidth = GRID_WIDTH) +
  geom_segment(
    data = item_spikes,
    mapping = aes(origin_1, origin_2, xend = end_1, yend = end_2),
    linewidth = LINE_WIDTH,
    linetype  = '43',
    color     = PALETTE_BLUE["light"]
  ) +
  geom_segment(
    arrow     = arrow(angle = 20, length = unit(10, "points"), type = "closed"),
    linejoin  = "mitre",
    linewidth = VECTOR_WIDTH
  ) +
  scale_x_continuous(
    limits       = c(-0.75, 1.5),
    breaks       = (-1:3)/2,
    minor_breaks = NULL,
    name         = NULL,
    expand       = expansion(),
    sec.axis     = dup_axis(name = "*&theta;*~2~", labels = NULL)
  ) +
  scale_y_continuous(
    limits       = c(-0.75, 1.5),
    breaks       = (-1:3)/2,
    minor_breaks = NULL,
    name         = NULL,
    expand       = expansion(),
    sec.axis     = dup_axis(name = "*&theta;*~1~", labels = NULL)
  ) +
  scale_color_manual(values = unname(PALETTE_BLUE["normal"]), guide = NULL) +
  annotate(
    "richtext",
    x = c(0.5, -0.1), y = c(-0.1, 1),
    label         = c("*a*~11~", "*a*~21~"),
    size          = 8,
    label.colour  = NA,
    label.padding = unit(0, "lines"),
    fill = NA
  ) +
  coord_fixed(clip = "on") +
  theme(
    axis.line          = element_blank(),
    axis.title         = element_markdown(size = 20, padding = unit(0, "lines")),
    axis.title.x       = element_markdown(hjust = 1/3),
    axis.title.y.right = element_markdown(vjust = 1/3),
    axis.ticks         = element_blank(),
    panel.grid.major   = element_line(
      linewidth = GRID_WIDTH,
      linetype  = "17"
    )
  )
```
:::

@@

::: fragment
$$
  \begin{align}
    MDISC^_1 &= \sqrt{
        [1, 1]
        \begin{bmatrix}
          1 \\
          1
        \end{bmatrix}
      } \\
      &= \sqrt{ 1 · 1 + 1 · 1 } \\
      &= \sqrt{ 1 + 1 } \\
      &= \sqrt{ 2 } \\
      &\approx 1.41
  \end{align}
$$
:::
:::::
:::::::
